### 2016-06-24 reasoning.tex
No more bashing [17].

The three \rulelabel{RG-Conseq} rules define ways to strengthen or
weaken relations and assertions associated with RG judgments of
transaction-bound expressions, commands and top-level commands,
respectively. In particular, they allow the precondition $P$ and the
rely relation $R$ to be strengthened\footnote{A stronger relation is a
smaller set than a weaker relation, hence a stronger $R$ admits lesser
interference than a weaker $R$}, and the postcondition $Q$ (also, $C$
in the case of expressions) and the guarantee relation $G$ to be
weakened. This kind of strengthening/weakening is also admitted in the
classical RG framework. The most notable aspect of
\rulelabel{RG-Conseq} rules however is that they allow the trace
invariant $\I$ to be strengthened. Considering that $\I$ captures
consistency and isolation properties, this means that a program proved
correct under weaker consistency and isolation levels is also correct
under stronger levels.  Parametricity over the trace invariant $\I$,
combined with the ability to strengthen $\I$ as needed, allows our
proof system to admit a highly flexible proof strategy to prove
programs correct on various stores. Unlike the existing approaches,
which require programs to be proved correct with respect to a
pre-defined store (\eg~A CC store in~\cite{gotsmanpopl16}), our
reasoning framework allows programmers to \emph{define} a store of
their choice (by defining $\I$ appropriately) and then prove programs
correct with respect to this store. Thus, programmers can prove their
programs correct with respect to an imaginary store that provides only
the required consistency and isolation guarantees. Soundness of
strengthening $\I$ guarantees that the program can now be executed
safely on any real store (\eg~a relational database, or a NoSQL store)
that offers same or stronger consistency and isolation guarantees as
the imaginary store. The following subsection proves the soundness of
our proof system.

@@

\GK{Here, I give intuitive explanation of soundness in the context of
EC replication. This answers Gustavo's question of why Gotsman-like
special case reasoning about replicas is not needed in our setting.}

>>>>

The three \rulelabel{RG-Conseq} rules define ways to strengthen or
weaken relations and assertions associated with RG judgments of
transaction-bound expressions, commands and top-level commands,
respectively. In particular, they allow the precondition $P$ and the
rely relation $R$ to be strengthened\footnote{A stronger relation is a
smaller set than a weaker relation, hence a stronger $R$ admits lesser
interference than a weaker $R$}, and the postcondition $Q$ (also, $C$
in the case of expressions) and the guarantee relation $G$ to be
weakened. This kind of strengthening/weakening is also admitted in the
classical RG framework. The most notable aspect of
\rulelabel{RG-Conseq} rules however is that they allow the trace
invariant $\I$ to be strengthened. Considering that $\I$ captures
consistency and isolation properties, this means that a program proved
correct under weaker consistency and isolation levels is also correct
under stronger levels.  Parametricity over the trace invariant $\I$,
combined with the ability to strengthen $\I$ as needed, allows our
proof system to admit a highly flexible proof strategy to prove
programs correct on various stores. Instead of requiring programs to
be proved correct with respect to a pre-defined store (\eg~A CC store
like in~\cite{gotsmanpopl16}), our reasoning framework allows
programmers to \emph{define} a store of their choice (by defining $\I$
appropriately) and then prove programs correct with respect to this
store. Thus, programmers can prove their programs correct with respect
to an imaginary store that provides only the required consistency and
isolation guarantees. Soundness of strengthening $\I$ guarantees that
the program can now be executed safely on any real store (\eg~a
relational database, or a NoSQL store) that offers same or stronger
consistency and isolation guarantees as the imaginary store. The
following subsection proves the soundness of our proof system.

@@
